graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-07-07 paper/paper.Rmd
correct grammar in paper

There is a need, therefore, for a systematic framework for statistical
modelling and simulation of gene expression data derived from
hypothetical, inferred or known gene networks. Here we present a
package to achieve this, where samples from a multivariate normal
distribution are used to generate normally-distributed log-expression
data, with correlations between genes derived from the structure of the
underlying pathway or gene regulatory network. This methodology enables
simulation of expression profiles that approximate the log-transformed
and normalised data from microarray studies, as well as, bulk or single-cell RNA-Seq
experiments. This procedure has been released as the \texttt{graphsim}
package to enable the generation of simulated gene expression datasets
containing pathway relationships from a known underlying network.
These simulated datasets can be used to evaluate various bioinformatics
methodologies, including
statistical and network inference procedures.

>>>>

There is a need, therefore, for a systematic framework for statistical
modelling and simulation of gene expression data derived from
hypothetical, inferred or known gene networks. Here we present a
package to achieve this, where samples from a multivariate normal
distribution are used to generate normally-distributed log-expression
data, with correlations between genes derived from the structure of the
underlying pathway or gene regulatory network. This methodology enables
simulation of expression profiles that approximate the log-transformed
and normalised data from microarray studies, as well as bulk or single-cell RNA-Seq
experiments. This procedure has been released as the \texttt{graphsim}
package to enable the generation of simulated gene expression datasets
containing pathway relationships from a known underlying network.
These simulated datasets can be used to evaluate various bioinformatics
methodologies, including
statistical and network inference procedures.
